Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
Update Checkpoint 4.Rmd
tables

```{r}
# model_15<-stan_glmer(
#   ChinaVirusInterest ~ (Day|State) + negative_rate, 
#   data=mod_data, family=gaussian, chains =4, iter = 5000
# )
```

```{r}
# head(data.frame(summary(model_15)),-2)
```

```{r}
# # Store the chains
# model_15_df <- as.array(model_15) %>% 
#   melt %>% 
#   pivot_wider(names_from = parameters, values_from = value)
# 
# # Wrangle the chains
# # Note the need for `...` around the sigma_sq_b
# model_15_df <- model_15_df %>% 
#   mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>% 
#   mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))
# 
# ggplot(model_15_df, aes(x = correlation)) + 
#   geom_density(alpha = 0.5)
```

@@

ggplot(model_16_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)
```

@@

>>>>

```{r}
model_15<-stan_glmer(
  ChinaVirusInterest ~ (Day|State) + negative_rate,
  data=mod_data, family=gaussian, chains =4, iter = 5000
)
```

```{r}
head(data.frame(summary(model_15)),-2)
```

```{r}
# Store the chains
model_15_df <- as.array(model_15) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_15_df <- model_15_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_15_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```

@@

ggplot(model_16_df, aes(x = correlation)) + 
  geom_density(alpha = 0.5)

@@

Model Outputs:

Model 14: 
ChinaVirusInterest~ (1|State) + negative_rate

mean	mcse	sd	X10.	X50.	X90.	n_eff	Rhat

44.38040197	0.11616343	4.2066034	39.0747590	44.36959567	49.6577069	1311	1.0010474
-4.03732266	0.13077873	4.8298203	-10.2151294	-4.12905314	2.2624868	1364	1.0007950

Model 16: 
ChinaVirusInterest~ (1|State) + percent_black + negative_rate

mean	mcse	sd	X10.	X50.	X90.	n_eff	Rhat

(intercept) 45.38818892	0.059114913	4.851982	39.1598750	45.42176405	51.6208513	6737	1.0001366
percent black -4.81756453	0.218542483	14.099591	-22.6838613	-5.02290077	13.1161595	4162	1.0008973
negative_rate -4.48821663	0.053252003	4.937795	-10.7851047	-4.47175240	1.7764630	8598	1.0002747
